Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-24 WSSSPE1_report/WSSSPE1_summary_report.tex
Added support info for Howison and tidied one or two sentences in the Policy section

These papers, and the discussion at the workshop, join a nascent
literature seeking to understand what drives software work in science
and how the reward systems of science thereby shape the type of
software work undertaken, including the extent to which developers are
motivated to build software for the long-term, for the use of others
and whether to work collaboratively or
separately~\cite{howison_incentives_2013, howison_scientific_2011,
  bietz_synergizing_2010}. Software work is not only motivated by
direct citations, but the visibility of software work in the
literature is important to those who write software used in science.

Papers and discussion concentrated on three overarching questions: How
ought software work to be visible, what are the barriers to its
visibility, and what can be done to make it more visible?

@@

>>>>

These papers, and the discussion at the workshop, join a nascent
literature seeking to understand what drives software work in science
and how the reward systems of science thereby shape the type of
software work undertaken. This study includes the extent to which developers are
motivated to build software for the long-term, for the use of others,
and whether to work collaboratively or
separately~\cite{howison_incentives_2013, howison_scientific_2011,
  bietz_synergizing_2010}. Software work is not only motivated by
direct citations, but the visibility of software work in the
literature is important to those who write software used in science.

Papers and discussion concentrated on three overarching questions: How
ought software work be visible, what are the barriers to its
visibility, and what can be done to make it more visible?

@@

Howison was supported by NSF SBE-1064209 and NSF ACI-0943168.
